### 2014-12-13 paper.tex
Add compactness threshhold and edit text to fit it

  Based on the data we have gathered, we propose the following court tests.  At a congressional level, districting plans for states with at least 3 districts are illegal if:
  \begin{itemize}
  \item A state plan has a voter efficiency gap greater than 20\% OR
  \item A state plan has a seat gap of greater than two seats OR
  \item%TODO: pick a compactness threshold, or a way to integrate in compactness
  \end{itemize}

  We believe that this accurately captures the most egregious of gerrymandering, as for states with at least 3 congressional districts, a 20\% threshold limit or 2 seat gap creates a balance to test for gerrymandering in both small and large states.  For small states, this could mean a seat distribution changing from 3-0 to 2-1, which is small on the grand scale, but possibly offers better representation within that state. Likewise, it can catch large states, who can have a strong influence on the overall makeup of Congress.  Based on our data, it would invalidate districting plans in Florida, Michigan, New Jersey, North Carolina, Ohio, Pennsylvania, Texas, and Virginia on the basis that they have a gap larger than two seats, and Connecticut and Nebraska, on the basis of having greater than a 20\% efficiency gap. Providing this criteria will allow the courts to effectively decide on gerrymandering cases.

>>>>

  Based on the data we have gathered, we propose an extension to the test of Stephanopoulos and McGhee~\cite{stephanopoulos}.  At a congressional level, we propose that districting plans for states with at least 3 districts be overturned if they have an efficiency gap of greater than 20\% or two seats, and also register poorly on at least one compactness metric: below $\frac23$ in the convex hull area metric, below $\frac34$ in the moment of area metric, or below $\frac23$ in the moment of population metric.  This weakens the standard

  We believe that this accurately captures the most egregious of gerrymandering, as for states with at least 3 congressional districts, a 20\% threshold limit or 2 seat gap creates a balance to test for gerrymandering in both small and large states.  For small states, this could mean a seat distribution changing from 3-0 to 2-1, which is small on the grand scale, but possibly offers better representation within that state. Likewise, it can catch large states, who can have a strong influence on the overall makeup of Congress.  Based on our data, it would invalidate districting plans in Michigan, New Jersey, North Carolina, Ohio, Pennsylvania, and Virginia on the basis that they have a gap larger than two seats and the requisite compactness.  A few other states, such as Connecticut and Nebraska, meet the partisan bias standard, but not the compactness standard, so they would not be invalidated.  Providing this criteria will allow the courts to effectively decide on gerrymandering cases.
